---
title: "Week 3 - Review of basics and data exploration"
author: "Dason Kurkiewicz"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Intro Activity
- Homework from last week

## Homework
- An R project simply a folder where all scripts, data, and other content related to your project will exist
- Using the command `getwd()` aka "get working directory" will tell you which folder or project you are in
- Think of projects like rooms in a house and all your project content is stuff in that room
    - If you ask for your water bottle and there is one in the room you are in, that is likely the water bottle you are talking about even if there is a water bottle in a different room
- You can also reference other folders inside of your room, i.e. (In my house, in the living room, in the bottom right desk drawer there is a piece of paper I need)
    - `home/livingRoom/desk/bottomRightDrawer/paper.txt`

    
## Starting a Project
- We are going to start a new project for this class
- File -> New Project
- New/Existing Directory
- Name
- Location
- Create a new script called `readingInData.R`

    
## Reading in Data
- Move the `Inventory.csv` file into your working directory
- Read `Inventory.csv` into R
    - Look at the head and tail of your data
    - How many rows does it have?
    - Let's look at Quantity
    - What is the largest value in your data?
    - What is the smallest value in your data?
    - What is the mean of your data?
    - What is the median of your data?
    - Did we run into any problems?
    
## Let's get help
- Did we run into any issues?
- How do we deal with NAs?
    
## Code

```{r activity_complete1, include=TRUE, echo=TRUE}
getwd()
shortPathName(getwd())

# I'll use an absolute path.
fileloc_inventory <- "C:/Users/kurkiewiczd/Projects/Learn-to-Code-in-R/Week 3 - Review and Data Exploration/Data/Inventory.csv"

```
## Code

```{r activity_complete2, include=TRUE, echo=TRUE}
inv <- read.csv(fileloc_inventory)
#inv <- readr::read_csv(fileloc_inventory)
head(inv)
tail(inv)
```
## Code
```{r activity_complete3, include=TRUE, echo=TRUE}
str(inv)
```
## Code
```{r activity_complete4, include=TRUE, echo=TRUE}
dim(inv)
nrow(inv)
ncol(inv)
```
## Code
```{r activity_complete6, include=TRUE, echo=TRUE}
hist(inv$Quantity)

```

## Code
```{r activity_complete5, include=TRUE, echo=TRUE}
table(inv$Quantity)

```

    
## Writing Data
- Convert Quantity so that it represents 1000s of units
- Write this new data to a file called `Inventory_Updated.csv`

## Working with selection
- Grabbing columns
- Grabbing rows
- Grabbing rows that meet certain conditions
- We have other ways to do this stuff but it's good to know base R
- tibble vs data.frame
- base R vs tidyverse

## Code
```{r activity_complete7, include=TRUE, echo=TRUE}
inv[1,]
inv[,1]
inv[1,1]
inv$Quantity[1]
inv[1, "Quantity"]
inv[which.max(inv$Quantity), ]
inv[inv$Quantity == max(inv$Quantity, na.rm = TRUE),]
inv[TRUE,]
inv[FALSE,]

```

## Getting Help
```{r activity_complete8, include=TRUE, echo=TRUE}
?max
#install.packages("pacman")
library(pacman)
?p_load
p_load
```